---
title: "Untitled"
author: "Yufei xia"
date: "2020/10/23"
output: pdf_document
---

---
title: "Earthquake research"
author: "Yufei xia"
date: "2020/10/2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)  # ggplot() fortify()
library(dplyr)  # %>% select() filter() bind_rows()
library(rgdal)  # readOGR() spTransform()
library(raster)  # intersect()
library(ggsn)  # north2() scalebar()
library(rworldmap)  # getMap()
```



```{r}
library(R.matlab)
library(caret)
library(e1071)
library(MASS)
library("RColorBrewer")
library(base)

```

```{r}
dateset <- readMat("EarlyWarning_Iwanuma_rev.mat")

```

```{r}
result = list()
```


# containing the details of employees 
# which can be done using a list command 
empList = list(empId, empName, numberOfEmp) 
  
```{r}
shit = list()
for(i in 5){
df = find_observations(100,5*i)
shit[i] =df
}
```

```{r}
work =  find_observations(100,5)
```


```{r}
#deal with the response variable.
find_observations = function(threshold, time){


#we might need multinomial distribution
loss = dateset$TL1.HS
dim(loss) = c(4000,1)
lon = dateset$SCENARIO[,2,]
dim(lon) = c(4000,1)
lat = dateset$SCENARIO[,3,]
dim(lat) = c(4000,1)
mag = dateset$SCENARIO[,1,]
dim(mag) = c(4000,1)
mag_level = rep(1:8,each = 500)




#set threshold
#under the threshold of 50
df = data.frame(loss)
df$category = cut(df$loss,breaks =c(-Inf, threshold, Inf),labels = c(0,1))
df$lon = lon
df$lat = lat 
df$mag = mag




#try to fit the logistic regression interm of longituted 
#the lat vs loss and the long vs loss





#train test split.
#we select the time = 60


coln = c()
set = (1:nrow(dateset$PntInfo))[dateset$PntInfo[,9]==3] 
for(i in set){
     observ_i = paste("observ",i,sep = "_")
     coln = c(coln, observ_i)
     matrix = apply(dateset$WHL1[1:time,i,,],c(2,3),function(x) max(x))
     dim(matrix) = c(4000,1)
     observ_i = matrix
     df = cbind(df, observ_i)
     
}


colnames(df)[6:98] = c(coln)


newdf = df[,-1]




set.seed(123)
sample_size = floor(0.8*nrow(newdf))
sample_inx = sample(1:nrow(newdf),size =sample_size,replace = FALSE)

train_sample = newdf[sample_inx,]
test_sample =newdf[-sample_inx,]


# Set seed for reproducibility
biggest = formula(glm(category~.,data = train_sample,family = binomial))
null_model=glm(category~lon+lat+mag,data= train_sample,family=binomial)
step_model = stepAIC(null_model, direction ="forward",scope = biggest,steps = 3)    


#fitting model with test data 
obs_point1 = names(step_model$model)[5]
obs_point2 = names(step_model$model)[6]
obs_point3 = names(step_model$model)[7]
formula1 = toString(paste("category~lon+lat+mag+", obs_point1))
formula2 = toString(paste("category~lon+lat+mag+", obs_point1,"+",obs_point2))
formula3 = toString(paste("category~lon+lat+mag+", obs_point1,"+",obs_point2,"+",obs_point3))
#test_model = glm(category~lon+lat+mag+obs_point1, data = test_sample,family = binomial)
origlnal_model = glm("category~lon+lat+mag",data = test_sample,family = binomial)
test_model = glm(formula1, data = test_sample,family = binomial)
test_model2 = glm(formula2, data = test_sample,family = binomial)
test_model3 = glm(formula3, data = test_sample,family = binomial)


#the accruacy and precision of test data.
predicted = predict(test_model,type = "response")
cate_predicted = cut(predicted, breaks =c(-Inf,0.5,Inf),labels = c(0,1))
true = test_sample$category
conf1 = confusionMatrix(cate_predicted,true)



predicted2 = predict(test_model2,type = "response")
cate_predicted2 = cut(predicted2, breaks =c(-Inf,0.5,Inf),labels = c(0,1))
true = test_sample$category
conf2 = confusionMatrix(cate_predicted2,true)


predicted3 = predict(test_model3,type = "response")
cate_predicted3 = cut(predicted3, breaks =c(-Inf,0.5,Inf),labels = c(0,1))
true = test_sample$category
conf3 = confusionMatrix(cate_predicted3,true)


 s1 = unlist(strsplit(obs_point1, split='_', fixed=TRUE))[2]
 colname = c()
 
#anova test 
test1 = anova(origlnal_model,test_model)
if((1-pchisq(test1$Deviance[2],test1$Df[2]))<0.05){
  s1 = unlist(strsplit(obs_point1, split='_', fixed=TRUE))[2]
  accu = conf1$byClass[11]
  sens = conf1$byClass[1]
  spec = conf1$byClass[2]
  datamessage1 = c(dateset$PntInfo[strtoi(s1),],accu,sens,spec)
  observations = data.frame(obs_point1 = datamessage1)
  colname=c(colname,obs_point1)
  
  
}
test2 = anova(test_model,test_model2)
if((1-pchisq(test2$Deviance[2],test2$Df[2]))<0.05){
  s2 = unlist(strsplit(obs_point2, split='_', fixed=TRUE))[2]
  accu = conf2$byClass[11]
  sens = conf2$byClass[1]
  spec = conf2$byClass[2]
  datamessage2 = c(dateset$PntInfo[strtoi(s2),],accu,sens,spec)
  
  observations$obs_point2 =datamessage2
  colname=c(colname,obs_point2)
  
  
}

test3 = anova(test_model2,test_model3)
if((1-pchisq(test3$Deviance[2],test3$Df[2]))<0.05){
  accu = conf3$byClass[11]
  sens = conf3$byClass[1]
  spec = conf3$byClass[2]
  s3 = unlist(strsplit(obs_point3, split='_', fixed=TRUE))[2]
  datamessage3 = c(dateset$PntInfo[strtoi(s3),],accu,sens,spec)
  observations$obs_point3 =datamessage3
  colname=c(colname,obs_point3)
  
}



colnames(observations) <- colname
}
```




```{r}
shit = list()
for(i in 5){
df = find_observations(100,5*i)
shit[i] =df
}
```

```{r}
work =  find_observations(100,5)
```


```{r}
#deal with the response variable.
find_observations = function(threshold, time){


#we might need multinomial distribution
loss = dateset$TL1.HS
dim(loss) = c(4000,1)
lon = dateset$SCENARIO[,2,]
dim(lon) = c(4000,1)
lat = dateset$SCENARIO[,3,]
dim(lat) = c(4000,1)
mag = dateset$SCENARIO[,1,]
dim(mag) = c(4000,1)
mag_level = rep(1:8,each = 500)




#set threshold
#under the threshold of 50
df = data.frame(loss)
df$category = cut(df$loss,breaks =c(-Inf, threshold, Inf),labels = c(0,1))
df$lon = lon
df$lat = lat 
df$mag = mag




#try to fit the logistic regression interm of longituted 
#the lat vs loss and the long vs loss





#train test split.
#we select the time = 60


coln = c()
set = (1:nrow(dateset$PntInfo))[dateset$PntInfo[,9]==3] 
for(i in set){
     observ_i = paste("observ",i,sep = "_")
     coln = c(coln, observ_i)
     matrix = apply(dateset$WHL1[1:time,i,,],c(2,3),function(x) max(x))
     dim(matrix) = c(4000,1)
     observ_i = matrix
     df = cbind(df, observ_i)
     
}


colnames(df)[6:98] = c(coln)


newdf = df[,-1]




set.seed(123)
sample_size = floor(0.8*nrow(newdf))
sample_inx = sample(1:nrow(newdf),size =sample_size,replace = FALSE)

train_sample = newdf[sample_inx,]
test_sample =newdf[-sample_inx,]


# Set seed for reproducibility
biggest = formula(glm(category~.,data = train_sample,family = binomial))
null_model=glm(category~lon+lat+mag,data= train_sample,family=binomial)
step_model = stepAIC(null_model, direction ="forward",scope = biggest,steps = 3)    


#fitting model with test data 
obs_point1 = names(step_model$model)[5]
obs_point2 = names(step_model$model)[6]
obs_point3 = names(step_model$model)[7]
formula1 = toString(paste("category~lon+lat+mag+", obs_point1))
formula2 = toString(paste("category~lon+lat+mag+", obs_point1,"+",obs_point2))
formula3 = toString(paste("category~lon+lat+mag+", obs_point1,"+",obs_point2,"+",obs_point3))
#test_model = glm(category~lon+lat+mag+obs_point1, data = test_sample,family = binomial)
origlnal_model = glm("category~lon+lat+mag",data = test_sample,family = binomial)
test_model = glm(formula1, data = test_sample,family = binomial)
test_model2 = glm(formula2, data = test_sample,family = binomial)
test_model3 = glm(formula3, data = test_sample,family = binomial)


#the accruacy and precision of test data.
predicted = predict(test_model,type = "response")
cate_predicted = cut(predicted, breaks =c(-Inf,0.5,Inf),labels = c(0,1))
true = test_sample$category
conf1 = confusionMatrix(cate_predicted,true)



predicted2 = predict(test_model2,type = "response")
cate_predicted2 = cut(predicted2, breaks =c(-Inf,0.5,Inf),labels = c(0,1))
true = test_sample$category
conf2 = confusionMatrix(cate_predicted2,true)


predicted3 = predict(test_model3,type = "response")
cate_predicted3 = cut(predicted3, breaks =c(-Inf,0.5,Inf),labels = c(0,1))
true = test_sample$category
conf3 = confusionMatrix(cate_predicted3,true)


 s1 = unlist(strsplit(obs_point1, split='_', fixed=TRUE))[2]
 colname = c()
 
#anova test 
test1 = anova(origlnal_model,test_model)
if((1-pchisq(test1$Deviance[2],test1$Df[2]))<0.05){
  s1 = unlist(strsplit(obs_point1, split='_', fixed=TRUE))[2]
  accu = conf1$byClass[11]
  sens = conf1$byClass[1]
  spec = conf1$byClass[2]
  datamessage1 = c(dateset$PntInfo[strtoi(s1),],accu,sens,spec)
  observations = data.frame(obs_point1 = datamessage1)
  colname=c(colname,obs_point1)
  
  
}
test2 = anova(test_model,test_model2)
if((1-pchisq(test2$Deviance[2],test2$Df[2]))<0.05){
  s2 = unlist(strsplit(obs_point2, split='_', fixed=TRUE))[2]
  accu = conf2$byClass[11]
  sens = conf2$byClass[1]
  spec = conf2$byClass[2]
  datamessage2 = c(dateset$PntInfo[strtoi(s2),],accu,sens,spec)
  
  observations$obs_point2 =datamessage2
  colname=c(colname,obs_point2)
  
  
}

test3 = anova(test_model2,test_model3)
if((1-pchisq(test3$Deviance[2],test3$Df[2]))<0.05){
  accu = conf3$byClass[11]
  sens = conf3$byClass[1]
  spec = conf3$byClass[2]
  s3 = unlist(strsplit(obs_point3, split='_', fixed=TRUE))[2]
  datamessage3 = c(dateset$PntInfo[strtoi(s3),],accu,sens,spec)
  observations$obs_point3 =datamessage3
  colname=c(colname,obs_point3)
  
}



colnames(observations) <- colname
return(observations)
}
```


```{r}
df1 = find_observations(20,5)
df2 = find_observations(20,10)
df3 = find_observations(20,15)
df4 = find_observations(20,20)
df5 = find_observations(20,25)
df6 = find_observations(20,30)
df7 = find_observations(20,35)
df8 = find_observations(20,40)
df9 = find_observations(20,45)
df10 = find_observations(20,50)
df11= find_observations(20,55)
df12= find_observations(20,60)



```

```{r}
finallist = list(df1,df2,df3,df4,df5,df6,df7,df8,df9,df10,df11,df12)
map_data = matrix(ncol = 2)
accrucy = c()
sensitivity = c()
specificity = c()
for (i in 1:12){
  dff = data.frame(finallist[i])
  if(i == 1){
    map_data = rbind(map_data, c(dff[7,1],dff[8,1]))
    map_data = rbind(map_data, c(dff[7,2],dff[8,2]))
    plot(1:2,c(dff[10,1],dff[10,2]),xlab= colnames(dff), ylab= "accuracy, sensitivity and specificity",type ="o",ylim =c(0.82,1),col = "red")
    lines(1:2,c(dff[11,1],dff[11,2]),type ="o",col = "green")
    lines(1:2,c(dff[12,1],dff[12,2]),type ="o",col = "blue")
    text(1.9, 0.97, "accruracy", cex = .8)
    text(1.9, 0.92, "sensitivity", cex = .8)
    text(1.9, 0.88, "specificity", cex = .8)
  }
  
  if (i != 1){
    map_data = rbind(map_data, c(dff[7,1],dff[8,1]))
    map_data = rbind(map_data, c(dff[7,2],dff[8,2]))
    map_data = rbind(map_data,c(dff[7,3],dff[8,3]))
    plot(1:3,c(dff[10,1],dff[10,2],dff[10,3]),xlab= colnames(dff),ylab="accuracy, sensitivity and specificity",type = "o",ylim =c(0.82,1),col = "red")
    lines(1:3,c(dff[11,1],dff[11,2],dff[11,3]),type ="o",col = "green")
    lines(1:3,c(dff[12,1],dff[12,2],dff[12,3]),type ="o",col = "blue")
    text(2.9, 0.97, "accruracy", cex = .8)
    text(2.9, 0.92, "sensitivity", cex = .8)
    text(2.9, 0.88, "specificity", cex = .8)
  }

  
  
}
map_data = map_data[-1,]
map_data = data.frame(map_data)
colnames(map_data) =c("lon","lat")
```

```{r}
library(mapdata)
library(ggplot2)
library(ggfortify)
map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
points(map_data$lat,map_data$lon, pch=19, col="red", cex=0.5)  #plot my sample sites

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[1])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[2])
points(dff[8,],dff[7,], pch=19, col="red", cex=1.2)#plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)


map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[3])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)


map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[4])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)


map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[5])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[6])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[7])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[8])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[9])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[10])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[11])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)

map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
dff = data.frame(finallist[12])
points(dff[8,],dff[7,], pch=19, col="red", cex=0.5)  #plot my sample sites
text(dff[8,],dff[7,],labels = colnames(dff),cex =0.3)
```



```

```{r}
map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
points(map_data$lat,map_data$lon, pch=19, col="red", cex=0.5)  #plot my sample sites

```
```{r}
for (i in 1:12){
  map("worldHires","Japan" , col="gray90",xlim=c(120,150),ylim=c(30,50) ,fill=TRUE)
  points(map_data$lat,map_data$lon, pch=19, col="red", cex=0.5)  #plot my sample sites
  
}
```

